---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# survTrial

<!-- badges: start -->
[![R-CMD-check](https://github.com/reevesj53/survTrial/workflows/R-CMD-check/badge.svg)](https://github.com/reevesj53/survTrial/actions)
<!-- badges: end -->

The goal of survTrial is to document common simulation methods used within biostatistics.  The current version of the package runs simulation scenarios for PFS, allowing for either:

* event times (progression and death) simulated from exponential distribution.
* death times simulated from exponential distribution, but progression times are moved forward to next   
  scheduled time and censored times are moved back to previous visit after random generation from   
  exponential.
  
Summary statistics for Kaplan-Meier medians and associated simulation graphs can be displayed for two treatment groups.  Similarly, simulation results for hazard ratio over all iterations of the trial design can be extracted.

## Installation

You can install the latest version of survTrial from [GitHub](https://github.com/) with:

``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("reevesj53/survTrial")
```
## Example
The code below shows examples of output from the simulations.

First, generate an example enrollment schedule in `enrol`, with ramp-up period of 5 months, 10 subjects per month thereafter leading to a total of 60 subjects with 1:1 randomization.

The visit schedule for tumor assessments is every 4 weeks (in `schedule`).  Median PFS for the two treatment groups (Treatment and Placebo) are 12 and 10 months respectively.

Data cut-off will occur at the 40th event.  
```{r example}
library(survTrial)

enrol <- c(seq(2,10,length.out=5),rep(10,times=3))
schedule <- seq(0,100,4)
rxrate <- c(12,10)
nevent <- 40

```
The proportion of events that are deaths is set at 10% and censoring rate is 10%.  We accept the default method of moving progression events forward to the next scheduled visit.  Then run the simulation:
```{r sim}
sim <- trial_sim(schedule, enrol, rxrate, nevent, adjust=TRUE, trt=c("treatment","placebo"),death.prop=0.1,
censor.prop=0.1,n.rep=1000)
```
The function `sim.km()` extracts both the simulated values for KM median by iteration and treatment group, and associated summary statistics by treatment group.  This information is shown below.
```{r calc_km}
sim.km <- calc_km(sim)
sim.km
```
A histogram plot of the simulated values for KM median can be obtained by calling `plot_sim()` for `sim.km` object. 
```{r plot1}
plot_sim(sim.km)
```
Additional options are available:

* add confidence bounds as specified in `calc_km()` (defaults to 95%) to the plot.
* add a table of summary statistics by treatment group.
```{r plot2}
plot_sim(sim.km, ci=TRUE, summary=TRUE)
```
Simulation results are also available for Hazard Ratio for each simulated trial by running the code below.
```{r calc_hr}
sim.hr <- calc_hr(sim)
```
And a similar graph of the simulation results for Hazard Ratio with associated summary table is obtained from the generic plotting function `plot_sim()`, as shown in the following:
```{r plot3}
plot_sim(sim.hr, ci=TRUE, summary=TRUE)
```
